Climate predictor selection and variable reduction methods influence MaxEnt model performance and predictions of climatic suitability

### 2023-06-05 manuscript/manuscript.tex
Correct section header formatting

\begin{keyword}
    Species distribution model \sep Variable selection \sep Ecological
model \sep 
    WORLDCLIM
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, enhanced, interior hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

@@

\hypertarget{methods-and-materials}{%
\section{2. Methods and materials}\label{methods-and-materials}}

\hypertarget{species-occurrence-records}{%
\subsubsection{Species occurrence
records}\label{species-occurrence-records}}

@@

\hypertarget{environmental-predictors}{%
\subsubsection{Environmental
predictors}\label{environmental-predictors}}

@@

\hypertarget{model-calibration}{%
\subsubsection{Model calibration}\label{model-calibration}}

@@

\hypertarget{model-evaluation}{%
\subsubsection{Model evaluation}\label{model-evaluation}}

@@

\hypertarget{model-visualisation}{%
\subsubsection{Model visualisation}\label{model-visualisation}}

@@

\hypertarget{results}{%
\section{3. Results}\label{results}}

\hypertarget{discussion}{%
\section{4. Discussion}\label{discussion}}

>>>>

\begin{keyword}
    Species distribution model \sep Variable selection \sep Ecological
model \sep 
    WORLDCLIM
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{methods-and-materials}{%
\section{Methods and materials}\label{methods-and-materials}}

\hypertarget{species-occurrence-records}{%
\subsection{Species occurrence
records}\label{species-occurrence-records}}

@@

\hypertarget{environmental-predictors}{%
\subsection{Environmental predictors}\label{environmental-predictors}}

@@

\hypertarget{model-calibration}{%
\subsection{Model calibration}\label{model-calibration}}

@@

\hypertarget{model-evaluation}{%
\subsection{Model evaluation}\label{model-evaluation}}

@@

\hypertarget{model-visualisation}{%
\subsection{Model visualisation}\label{model-visualisation}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}
